### 2021-12-10 draft.tex
Deploying to gh-pages from @ PoisotLab/ms_networkary_classifiers@9364d894c21b55736a0bd2d767725ff8e5523f1e 🚀

\begin{figure}
\hypertarget{fig:analytics}{%
\centering
\includegraphics{figures/analytics.png}
\caption{Consequences of changing the classifier skills (\(s\)) and bias
(\(s\)) for a connectance \(\rho=0.15\), on accuracy, \(F_1\), postive
predictive value, and \(\kappa\). \textbf{TODO} discussion of
results}\label{fig:analytics}
}
\end{figure}

>>>>

\begin{figure}
\hypertarget{fig:analytics}{%
\centering
\includegraphics{figures/analytics.png}
\caption{Consequences of changing the classifier skills (\(s\)) and bias
(\(s\)) for a connectance \(\rho=0.15\), on accuracy, \(F_1\), postive
predictive value, and \(\kappa\). Accuracy increases with skill, but
also increases when the bias tends towards estimating \emph{fewer}
interactions. The \(F_1\) score increases with skill but also increases
when the bias tends towards estimating \emph{more} interactions; PPV
behaves in the same way. Interestingly, \(\kappa\) responds as expected
to skill (being negative whenever \(s < 0.5\)), and peaks for values of
\(b \approx 0.5\); nevertheless, the value of bias for which \(\kappa\)
is maximized in \emph{not} \(b=0.5\), but instead increases with
classifier skill. In other words, at equal skill, maximizing \(\kappa\)
would lead to select a \emph{more} bias
classifier.}\label{fig:analytics}
}
\end{figure}
